Paper 2 !DRAFT! Do not circulate!

### 2015-01-05 Articles/Article_EcolEcon_2014/Paper2.Rnw
Added text about uncertainty of CES parameters.

>>>>

Certain combinations of economy, parameter values, CES nesting structure, and data source
come with very large resampling spreads, 
indicating large fitted parameter uncertainties. 
Often, there is virtually no useful information 
in $\delta$, $\delta_1$, $\alpha$, $\beta$, and $\gamma$.

Thus, we find that nesting has significant influence on model results.

That so many estimates of elasticity of substitution exhibit large uncertainty, 
often spanning the range from perfect complements ($\sigma, \, \sigma_1 = 0$) 
to perfect substitutes ($\sigma, \, \sigma_1 = \infty$), 
is a troubling characteristic of the estimated CES coefficients 
that is rarely investigated in the literature.
Indeed, for some economies, 
estimating any elasticity of substitution at all is problematic and fraught with peril. 
Earlier, we noted that 
even when residuals for the fit to historical data are small 
and the model produces fitted values that track the historical data closely, 
it may yet be difficult to estimate some or all of the model parameters precisely.
That appears to be the case for 
values of $\rho$ and $\rho_1$ and associated
elasticities of substitution~($\sigma$ and $\sigma_1$)
in the CES production function.
Note that this result is unlikely to be caused by poor-quality data alone. 
Elasticities of substitution for the economies with presumably the best data in the world 
(United States, United Kingdom, Japan, and Austria) exhibit large uncertainty.

Some of the uncertainty in parameter estimates is explained by 
the mathematical structure of the CES model itself. 
Equations~\ref{eq:CES}--\ref{eq:CESekl} indicate that 
if $\delta$ or $\delta_1$ achieves an extreme value (0 or 1), 
the corresponding elasticity of substitution ($\sigma$ or $\sigma_1$) becomes meaningless. 
If $\delta$ approaches unity, values of $\delta_1$ and $\sigma_1$ become meaningless.
Thus, large uncertainty in $\sigma$, $\sigma_1$, and $\delta_1$ can be expected for any CES model 
in which parameter estimates are positioned on the left or right boundaries
of Figures~\ref{fig:CES_sigma1_delta1_graph} or~\ref{fig:CES_sigma_delta_graph}.

Some of the uncertainty in parameter estimates may be explained by structural change 
in the economies over the time period under study (1960--2011). 
To account for the large uncertainty, 
it may be useful to perform piecewise analyses of smaller time periods.
